Adolescent well-being in the digital age

### 2022-01-27 01-timecourses.qmd
Save correlation parameter docx table

```{r setup}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(ggstance)
library(mgcv)
library(brms)
library(cmdstanr)
library(ellipse)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(emmeans)
library(broom)
library(tidyverse)
```

@@

```{r fitted-trend-country}
f_country <- fits %>%
  mutate(fc = map(fit1, fitted_country)) %>%
  select(outcome, fc)

# Create the plot for each outcome
f_country <- f_country %>%
  mutate(
    plot = map2(
      fc, outcome,
      ~ plot_country(.x, .y)
    )
  )
```

@@

```{r trends-ls}
#| echo: false
#| fig-width: 12
#| fig-height: 10
#| fig-cap: "Life satisfaction trends, ordered by association magnitude"
#| label: fig-trends-ls
f_country$plot[[1]]
```

@@

>>>>

```{r setup}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(ggstance)
library(mgcv)
library(cmdstanr)
library(officer)
library(ellipse)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(emmeans)
library(broom)
library(brms)
library(tidyverse)
```

@@

@@

```{r trends-ls}
f_country <- fits %>%
  mutate(fc = map(fit1, fitted_country)) %>%
  select(outcome, fc)

# Create the plot for each outcome
f_country <- f_country %>%
  mutate(
    plot = map2(
      fc, outcome,
      ~ plot_country(.x, .y)
    )
  )
#| echo: false
#| fig-width: 12
#| fig-height: 10
#| fig-cap: "Life satisfaction trends, ordered by association magnitude"
#| label: fig-trends-ls
f_country$plot[[1]]
```

@@

```{r}
# Display table and print in word document
cor_tab <- cor_pars %>% 
  transmute(
    outcome = str_replace(outcome, "_", " "), 
    correlation = str_glue("{mean} [{q2.5}, {q97.5}]")
  )
cor_tab %>%   
  kbl(caption = "Between-country trend correlation parameters") %>% 
  kable_custom()

read_docx() %>% 
  body_add_table(
    cor_tab,
    first_column = TRUE
  ) %>% 
  print("Table-correlations.docx")
```
